---
title: "Final Project"
author: "Ambar Flores, Amna Malik "
date: "Data 2401"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse) 
library(ggplot2) 
library(lubridate)
```


```{r}
airline <- read.csv("Airlines Reviews and Rating.csv")
head(airline)
```
## **summary**

This dataset from Kaggle has reviews and ratings about airlines. It's got feedback on things like flights, service, and more. People can use it to see how happy passengers are with different airlines and figure out how to make things better. It's useful for the travel industry and anyone who wants to predict how satisfied customers will be.


This dataset offers a overall view of air travel experiences by not only detailing the type of aircraft in use but also providing ratings for staff performance and overall flight experience, scored on a scale from 1 to 5. In today's aviation landscape, where concerns like the reliability of Boeing aircraft have come to the forefront due to pre-flight breakdowns, being able to discern the type of plane is concequencial for consumers making travel decisions. Moreover, the dataset sheds light on an important aspect often overlooked: the discrepancy between an airline's overall reputation and the quality of its customer service. By providing such nuanced insights, this dataset encourages consumers to play a more active role in their travel choices, prioritizing safety and comfort over mere convenience or brand reputation. It serves as a tool for informed decision-making, ensuring that passengers have the necessary information to make choices that align with their preferences and priorities.


## **Questions**

Which airline has the best customer service?

```{r}
best_customer_service <- airline %>%
  group_by(Country) %>%
  summarize(averagecustomerservice = mean(Cabin.Staff.Service, na.rm = TRUE)) %>%
  arrange(desc(averagecustomerservice))

best_customer_service %>% knitr::kable()

```


How many Planes are Boeing planes?

```{r}
boeing_planes <- airline %>%
  filter(str_detect(Aircraft.Type, "Boeing"))

n_boeing_planes <- nrow(boeing_planes)

n_boeing_planes

```


Does business class have better accommodation compare to economy? 
```{r}
# Filter data for business class
business_class <- airline %>%
  filter(Seat_Types == "Business Class")

# Filter data for economy class
economy_class <- airline %>%
  filter(Seat_Types == "Economy Class")

# Calculate average ratings for each amenity in business class
avg_ratings_business <- business_class %>%
  summarize(avg_seat_comfort = mean(Seat.Comfort, na.rm = TRUE),
            avg_cabin_staff_service = mean(Cabin.Staff.Service, na.rm = TRUE),
            avg_ground_service = mean(Ground.Service, na.rm = TRUE),
            avg_food_beverages = mean(Food...Beverages, na.rm = TRUE))

# Calculate average ratings for each amenity in economy class
avg_ratings_economy <- economy_class %>%
  summarize(avg_seat_comfort = mean(Seat.Comfort, na.rm = TRUE),
            avg_cabin_staff_service = mean(Cabin.Staff.Service, na.rm = TRUE),
            avg_ground_service = mean(Ground.Service, na.rm = TRUE),
            avg_food_beverages = mean(Food...Beverages, na.rm = TRUE))

# Print the results
avg_ratings_business
avg_ratings_economy

```

What is the difference between Economy and Buiness class ex:food bev, wifi, inflight entertainment ect.

```{r}

# amenity in business class
avg_ratings_business <- business_class %>%
  summarize(avg_seat_comfort = mean(Seat.Comfort, na.rm = TRUE),
            avg_cabin_staff_service = mean(Cabin.Staff.Service, na.rm = TRUE),
            avg_ground_service = mean(Ground.Service, na.rm = TRUE),
            avg_food_beverages = mean(Food...Beverages, na.rm = TRUE))

#  amenity in economy class
avg_ratings_economy <- economy_class %>%
  summarize(avg_seat_comfort = mean(Seat.Comfort, na.rm = TRUE),
            avg_cabin_staff_service = mean(Cabin.Staff.Service, na.rm = TRUE),
            avg_ground_service = mean(Ground.Service, na.rm = TRUE),
            avg_food_beverages = mean(Food...Beverages, na.rm = TRUE))

differences <- avg_ratings_business - avg_ratings_economy

differences

differences_long <- differences %>%
  pivot_longer(cols = everything(), names_to = "Amenity", values_to = "Difference")


differences_plot <- ggplot(differences_long, aes(x = Amenity, y = Difference, fill = Amenity)) +
  geom_bar(stat = "identity") +
  labs(title = "Differences Between Economy and Business Class Amenities",
       x = "Amenity",
       y = "Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")

#plot
print(differences_plot)
```

which country has the best flights?

```{r}


```

